Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-05-15 paper/ms.tex
Changes based on PT comments

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which are exceptionally
gas-poor to be rotating very slowly. We therefore predict that observations
which target such galaxies (e.g., lenticular barred
galaxies\cite{2009ARAA..47..159B}) would find slowly rotating bars. There does
exist one such example of a galaxy which is known to be a slow rotator -- the
low surface brightness galaxy UGC 628.\cite{2009AA...499L..25C} This galaxy
has been studied in detail by ref.\cite{2016MNRAS.463.1751C}, who note that it
indeed has a low gas fraction for galaxies of its type. In general, we predict
that bars in gas-rich spiral galaxies should rotate quickly while bars in
gas-poor spiral galaxies should rotate slowly.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, David~N. Spergel, Martin~D. Weinberg, and Yanfei Zou for
helpful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. Some computations in this paper were run on the FASRC Cannon
cluster supported by the FAS Division of Science Research Computing Group at
Harvard University. Resources supporting this work were also provided by the
NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing
(NAS) Division at Ames Research Center. A.B. was supported by the Future
Investigators in NASA Earth and Space Science and Technology (FINESST) award
number 80NSSC20K1536 during the completion of this work. L.H. funding. E.D.
funding. F.M. funding. C.C. funding. J.Q. acknowledges support from NSF grant AST-2008490. L.V.S. funding. PT acknowledges support from NSF grant AST-1909933, AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges support through NASA ATP 19-ATP19-0019,
19-ATP19-0020, 19-ATP19-0167, and NSF grants AST-1814053, AST-1814259,
AST-1909831, AST-2007355 and AST-2107724.

@@

Star formation occurs in cells above a density threshold
($n_{\textrm{th}}=100\,\textrm{cm}^{-3}$) according to
ref.\cite{2003MNRAS.339..289S} with a star-formation efficiency of $\epsilon =
0.01$. Star formation converts gas cells into star particles which represent
single stellar populations. For each star particle, the deposition of energy,
momentum, and mass from stellar winds and supernovae is modeled.
Photo-ionization and radiation pressure are modeled using an approximate
treatment. A more detailed description of this model can be found in the
flagship SMUGGLE paper.\cite{2019MNRAS.489.4233M}

>>>>

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which have been gas-poor for
extended periods of time to be rotating very slowly. We therefore predict that
observations which target such galaxies (e.g., lenticular barred
galaxies\cite{2009ARAA..47..159B}) would find slowly rotating bars. There does
exist one such example of a galaxy which is known to be a slow rotator -- the
low surface brightness galaxy UGC 628.\cite{2009AA...499L..25C} This galaxy
has been studied in detail by ref.\cite{2016MNRAS.463.1751C}, who note that it
indeed has a low gas fraction for galaxies of its type. We predict a general
trend that bars in gas-rich spiral galaxies should rotate quickly while bars
in gas-poor spiral galaxies should rotate slowly.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, Martin~D. Weinberg, and Yanfei Zou for helpful discussions.
A.B. would like to thank Todd Phillips for helpful discussions. Some
computations in this paper were run on the FASRC Cannon cluster supported by
the FAS Division of Science Research Computing Group at Harvard University.
Resources supporting this work were also provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center. A.B. was supported by the Future
Investigators in NASA Earth and Space Science and Technology (FINESST) award
number 80NSSC20K1536 during the completion of this work. L.H. funding. E.D.
funding. F.M. funding. C.C. funding. J.Q. acknowledges support from NSF grant
AST-2008490. L.V.S. funding. P.T. acknowledges support from NSF grant
AST-1909933, AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges
support through NASA ATP 19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF
grants AST-1814053, AST-1814259, AST-1909831, AST-2007355 and AST-2107724.

@@

Star formation occurs in cells above a density threshold
($n_{\textrm{th}}=100\,\textrm{cm}^{-3}$) with a star-formation efficiency of
$\epsilon = 0.01$. Star formation converts gas cells into star particles which
represent single stellar populations. For each star particle, the deposition
of energy, momentum, and mass from stellar winds and supernovae is modeled.
Photo-ionization and radiation pressure are modeled using an approximate
treatment. A more detailed description of this model can be found in the
flagship SMUGGLE paper.\cite{2019MNRAS.489.4233M}
